---
title: Short Paper
subtitle: A Short Subtitle
author:
  - name: Emilio García
    email: 319227105@enesmerida.unam.mx
    affiliations: 
        - id: UNAM
          name: Universidad Nacional Autónoma de México
          department: ENES Merida
          address: Mérida-Tetiz
          city: Merida
          state: Yucatán
          postal-code: 97357
    attributes:
        corresponding: true
    note: This is the first author footnote.
  - name: Miguel Güemez
    email: 422003010@enesmerida.unam.mx
    affiliations:
        - id: UNAM
          name: Universidad Nacional Autónoma de México
          department: ENES Merida
          address: Mérida-Tetiz
          city: Merida
          state: Yucatán
          postal-code: 97357
    note: |
      Another author footnote, this is a very long footnote and it should be a really long footnote. But this footnote is not yet sufficiently long enough to make two lines of footnote text.

lang: es
cap-location: bottom
abstract: |
  El presente estudio es enfocado a conocer y comparar la diversidad de especies de peces en dos sitios dentro del Estado de Yucatán con diferentes condiciones ambientales, Dzilam de Bravo y El Cuyo. Se utilizó el protocolo AGRRA para muestreo de peces en ambos sitios y en dos tiempos: mañana y tarde. Los resultados mostraron una diferencia en las especies observadas tanto en  espacio como en tiempo [(sin embargo) fueron o no significativas]. Este estudio provee de una base para la investigación, programas de coservación y manejo de recursos. Se recomienda para futuros trabajos 
keywords: 
  - keyword1
  - keyword2
date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: super
editor: 
  markdown: 
    wrap: 72
---

Please make sure that your manuscript follows the guidelines in the
Guide for Authors of the relevant journal. It is not necessary to
typeset your manuscript in exactly the same way as an article, unless
you are submitting to a camera-ready copy (CRC) journal.

For detailed instructions regarding the elsevier article class, see
<https://www.elsevier.com/authors/policies-and-guidelines/latex-instructions>

# Introducción

Los sistemas costeros son unos de los más afectados por las actividades
humanas, especialmente porque hay una tendencia que favorece el
desarrollo de nucleos poblacionales cercanos a la costa debido a que
facilita actividades como el turismo y la pesca @barragán2015 en
especifico para estas dos actividades es importante conocer la
biodiversidad de los sistemas marinos para poder aprovecharlos y
conservarlos adecuadamente. Los peces en particular son un grupo de
organismos muy conocido y abundante, tanto que representan casi la mitad
de las especies de vertebrados a escala global @bingpeng2018 resaltando
así su importancia tanto en sistemas naturales como para la provisión de
servicios ecosistémicos @rönnbäck2007. Por estas razones, es imperante
conocer los factores que moldean la composición de especies; en el caso
de sistemas acuáticos, el sustrato juega un papel esencial, ya la
mayoría de los organismos utilizan un componente de este en algún punto
de su ciclo de vida @rönnbäck2007. Uno de los componentes más
importantes del sustrato es la vegetación que lo acompaña. Este estudio
se centra en caracterizar la diversidad de peces en la zona costera,
para lo cual comparamos dos sitios: Dzilam de Bravo y El Cuyo; siendo la
vegetación una caracteristica altamente contrastante, ya que el cuyo al
ser una zona relativamente más conservada, no está asociado a las
grandes coberturas de pastos marinos como las que se ven en Dzilam de
Bravo, un sitio más perturbado.

# Bibliography styles

Here are two sample references: @Feynman1963118 @Dirac1953888

By default, natbib will be used with the `authoryear` style, set in
`classoption` variable in YAML. You can sets extra options with
`natbiboptions` variable in YAML header. Example

```         
natbiboptions: longnamesfirst,angle,semicolon
```

There are various more specific bibliography styles available at
<https://support.stmdocs.in/wiki/index.php?title=Model-wise_bibliographic_style_files>.
To use one of these, add it in the header using, for example,
`biblio-style: model1-num-names`.

## Using CSL

If `cite-method` is set to `citeproc` in `elsevier_article()`, then
pandoc is used for citations instead of `natbib`. In this case, the
`csl` option is used to format the references. By default, this template
will provide an appropriate style, but alternative `csl` files are
available from <https://www.zotero.org/styles?q=elsevier>. These can be
downloaded and stored locally, or the url can be used as in the example
header.

# Equations

Here is an equation: $$ 
  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
  \left(\frac{x}{\beta}\right)^{\alpha-1}
  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
  \alpha,\beta,x > 0 .
$$

Inline equations work as well: $\sum_{i = 2}^\infty\{\alpha_i^\beta\}$

# Figures and tables

@fig-meaningless is generated using an R chunk.

```{r}
#| label: fig-meaningless
#| fig-cap: A meaningless scatterplot
#| fig-width: 5
#| fig-height: 5
#| fig-align: center
#| out-width: 50%
#| echo: false
plot(runif(25), runif(25))
```

# Tables coming from R

Tables can also be generated using R chunks, as shown in @tbl-simple
example.

```{r}
#| label: tbl-simple
#| tbl-cap: Caption centered above table
#| echo: true
knitr::kable(head(mtcars)[,1:4])
```

# References {.unnumbered}
